A generic and fast C++ optimization framework

### 2017-10-17 paper.tex
Add first optimizer.
Refactor introduction, fill in blank pieces.
I'm ok with this; maybe it can be improved but this is at least an ok start.

In recent times, machine learning conferences have focused more and more on
optimization techniques.  For instance, this year at ICML (ICML 2017), every
single session had at least one track devoted solely to optimization
techniques.
<TODO: add some more filler here.  Show that optimization is an important part
of machine learning, in whatever ways.>

\begin{itemize}
  \item This sequence of events (or situation) motivates the development of a
generic, flexible, and fast optimization framework.
  \item We have implemented exactly this in {\bf mlpack}, and it's good.
\end{itemize}

{\bf <TODO: elaborate on above, add a few more sentences.>}

{\bf <TODO: mention related work, or really that we haven't found other
libraries that have a comprehensive infrastructure like the one we have built,
and that what we have built is more flexible and generic}

@@

\begin{itemize}
  \item {\bf <TODO: add all optimizers>}
  \item {\bf <TODO: add all things that we can optimize>}
\end{itemize}

@@

>>>>

Machine learning is a field that is inextricably intertwined with the field of
optimization.  Countless machine learning techniques depend on the optimization
of a given objective function; for instance, classifiers such as logistic
regression \cite{cox1958regression}, metric learning methods like NCA
\cite{goldberger2005neighbourhood}, manifold learning algorithms like MVU
\cite{weinberger2006introduction}, and the extremely popular field of deep
learning \cite{schmidhuber2015deep}.  Thanks to the attention focused on these
problems, it is increasingly important in the field to have fast, practical
optimizers.  This can explain the current focus on optimization: this year at
ICML (2017), every single session had at least one track devoted solely to
optimization techniques.

Therefore, the need is real to provide a robust, flexible framework in which
new optimizers can be easily developed.  Similarly, the need is also real for a
flexible framework that allows new objective functions to be easily implemented
and optimized with a variety of possible optimizers.

However, the current landscape of optimization frameworks for machine learning
is not particularly comprehensive.  A variety of tools such as
Caffe \cite{jia2014caffe},
% mxnet ??
TensorFlow \cite{abadi2016tensorflow},
and
Keras \cite{chollet2015}
have optimization frameworks, but they are limited to SGD-type optimizers and
only are able to optimize deep neural networks or related structures.  Thus
expressing arbitrary machine learning objective functions can be difficult or in
some cases not possible.  Other libraries, like
% Shogun \cite{shogun}
%and
scikit-learn \cite{pedregosa2011scikit},
do have optimizers implementation, but generally not in a coherent framework and
often the implementations may be specific to an individual machine learning
algorithm.  At a higher level, many programming languages may have generic
optimizers, like SciPy \cite{jones2014scipy} and MATLAB, but typically these
optimizers are not suitable for large-scale machine learning tasks where, e.g.,
calculating the full gradient of all of the data may not be feasible.

Given this situation, we have developed a flexible optimization infrastructure
in the {\bf mlpack} C++ machine learning library \cite{mlpack2013}.  This
infrastructure makes it easy to combine nearly any type of optimizer with nearly
any type of objective function, and has allowed us to minimize the effort
necessary to both implement new optimizers and to implement new machine learning
algorithms that depend on optimization.  Since the framework is implemented in
C++ and uses template metaprogramming, we are able to preserve a clean syntax
while simultaneously allowing compile-time optimizations that can result in a
generic optimizer that is equivalently fast to an optimizer written specifically
for one objective function.

In this short paper, we describe mlpack's optimization infrastructure in detail.
First, we describe the types of optimization problems we would like to solve,
which then allows us to build a generic and intuitive API for objective
functions to implement and optimizers to depend upon.  We show a very simple
example objective function and optimizer, and a system that we have built to
detect when a user passes an objective function that cannot be optimized by a
certain optimizer.  Lastly, we show the optimizers we have implemented in this
framework, and some example usage of mlpack's optimizers.

%In recent times, machine learning conferences have focused more and more on
%optimization techniques.  For instance, this year at ICML (ICML 2017), every
%single session had at least one track devoted solely to optimization
%techniques.
%<TODO: add some more filler here.  Show that optimization is an important part
%of machine learning, in whatever ways.>

%\begin{itemize}
%  \item This sequence of events (or situation) motivates the development of a
%generic, flexible, and fast optimization framework.
%  \item We have implemented exactly this in {\bf mlpack}, and it's good.
%\end{itemize}

%{\bf <TODO: elaborate on above, add a few more sentences.>}

%{\bf <TODO: mention related work, or really that we haven't found other
%libraries that have a comprehensive infrastructure like the one we have built,
%and that what we have built is more flexible and generic}

@@

% I guess to save some space we should group them.
\begin{itemize}
  \item {\bf SGD variants:} Vanilla SGD, SCD, SGDR, SMORMS3, AdaGrad, AdaDelta, RMSProp, Adam, AdaMax
  \item {\bf Quasi-Newton variants:} LBFGS, IQN, AugLagrangian
  \item {\bf Genetic variants:} CNE, CMA-ES
  \item {\bf Simulated Annealing}: Vanilla SA
  \item {\bf <TODO: add all things that we can optimize>}
\end{itemize}

@@

\bibliographystyle{plain}
\bibliography{paper}
